A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-07-11 results.tex
Update on Overleaf.
rm unharmonized sector

MESSAGE-GLOBIOM includes a representation of 11 distinct regions which can be
mapped directly to the 5-region definition used in the RCPs. Historical data is
taken from previously described LUC and anthropogenic sources, which comprise 10
separate pollutant and GHG species and 13 sectors shown in Table
\ref{tab:sp}. Therefore, a total of 1430 distinct trajectories were harmonized
for each scenario.

\begin{table}[]
  \centering
  \caption{Harmonized Species and Sectors}
  \label{tab:sp}
  \begin{tabular}{|l|l|}
    \hline
    \textbf{Emissions Species}        & \textbf{Sectors}                    \\
    \hline
    Black Carbon (BC)                 & Agricultural Waste Burning          \\
    Hexafluoroethane (C2F6)           & Agriculture                         \\
    Tetrafluoromethane (CF4)          & Aircraft                            \\
    Methane (CH4)                     & Energy Sector                       \\
    Carbon Dioxide (CO2)              & Forest Burning                      \\
    Carbon Monoxide (CO)              & Grassland Burning                   \\
    Hydrofluorocarbons (HFCs)         & Industrial Sector                   \\
    Nitrous Oxide (N2O)               & International Shipping              \\
    Ammonia (NH3)                     & Residential Commercial Other        \\
    Nitrogen Oxides (NOx)             & Solvents Production and Application \\
    Organic Carbon (OC)               & Transportation Sector               \\
    Sulfur Hexafluoride (SF6)         & Unharmonized                        \\
    Sulfur Oxides (SOx)               & Waste                               \\
    Volatile Organic Compounds (VOCs) &                                     \\
    \hline
  \end{tabular}
\end{table}

@@

Figure \ref{fig:co} presents a case in which the magnitude of a trajectory is
distorted. A large discrepancy ($\sim$300\% relative difference) is
observed in the harmonization year for carbon monoxide (CO) emissions in the
industrial sector specifically for the South Asia (SAS) MESSAGE-GLOBIOM region,
which comprises most of the Asian subcontinent. The default method chosen
(\code{constant_ratio}) maintains model trends for the region; however, overall
model results are distorted. By applying a \code{constant_offset} override, the
regional trend and magnitude is maintained. With the new harmonization method
for the SAS region, the global trajectory for industrial CO also corresponds
more closely with the unharmonized trajectory.

@@

In certain circumstances, the application of the default harmonization methods
can affect not only the magnitude but also the shape of regional
trajectories. Figure \ref{fig:nh3} shows an example case of emissions
trajectories for ammonia (NH3) from the agriculture sector in Asia. Again, the
SAS region shows a large discrepancy in the harmonization year ($>$150\% in
this case). The resulting trajectory harmonized with the default method
(\code{constant_ratio}) provides a large increase after 2080 in the SSP2
reference scenario. Notably, the SSP2-45 scenario is not affected to the same
degree. While this distortion changes the magnitude of the SAS trajectory, it
largely affects the post-2080 shape of the global trajectory (see Figure
\ref{fig:nh3}, panel \textbf{c}). By using a \code{constant_offset} method as an
override, this distortion is addressed and more accurately reflects unharmonized
results both in the SAS region and global results for agricultural ammonia
emissions.

>>>>

MESSAGE-GLOBIOM includes a representation of 11 distinct regions which can be
mapped directly to the 5-region definition used in the RCPs. Historical data is
taken from previously described LUC and anthropogenic sources, which comprise 10
separate pollutant and GHG species and 12 sectors shown in Table
% * <maarten.vandenberg@pbl.nl> 2017-07-03T22:41:59.852Z:
% 
% >  which comprise 10
% > separate pollutant and GHG species and 13 sectors shown in Table
% Do we correctly distinguish between the regional and global values (N2O)? The table mentions a sector "Unharmonized", which is the sector-aggregated value I assume, which also might lead to overcounting. In the table I would change this sector naming.
% 
% ^.
\ref{tab:sp}. Therefore, a total of 1430 distinct trajectories were harmonized
for each scenario.

\begin{table}[]
  \centering
  \caption{Harmonized Species and Sectors}
  \label{tab:sp}
  \begin{tabular}{|l|l|}
    \hline
    \textbf{Emissions Species}        & \textbf{Sectors}                    \\
    \hline
    Black Carbon (BC)                 & Agricultural Waste Burning          \\
    Hexafluoroethane (C2F6)           & Agriculture                         \\
    Tetrafluoromethane (CF4)          & Aircraft                            \\
    Methane (CH4)                     & Energy Sector                       \\
    Carbon Dioxide (CO2)              & Forest Burning                      \\
    Carbon Monoxide (CO)              & Grassland Burning                   \\
    Hydrofluorocarbons (HFCs)         & Industrial Sector                   \\
    Nitrous Oxide (N2O)               & International Shipping              \\
    Ammonia (NH3)                     & Residential Commercial Other        \\
    Nitrogen Oxides (NOx)             & Solvents Production and Application \\
    Organic Carbon (OC)               & Transportation Sector               \\
    Sulfur Hexafluoride (SF6)         & Waste                               \\
    Sulfur Oxides (SOx)               &                                     \\
    Volatile Organic Compounds (VOCs) &                                     \\
    \hline
  \end{tabular}
\end{table}

@@

Figure \ref{fig:co} presents a case in which the magnitude of a trajectory is
distorted. A large discrepancy ($\sim$300\% relative difference) is
observed in the harmonization year for carbon monoxide (CO) emissions in the
industrial sector specifically for the South Asia (SAS) MESSAGE-GLOBIOM region,
which comprises most of the Asian subcontinent. The default method chosen
(\code{constant_ratio}) maintains model trends for the region; however, overall
model results are distorted. By applying a \code{constant_offset} override, the
regional trend and magnitude is maintained. With the new harmonization method
for the SAS region, the global trajectory for industrial CO also corresponds
more closely with the unharmonized trajectory.
% * <maarten.vandenberg@pbl.nl> 2017-07-03T22:53:14.757Z:
% 
% > the global trajectory for industrial CO also corresponds
% > more closely with the unharmonized trajectory.
% The global trajectory suffers under the constant_ratio method from changing relative importance of underlying regions, resulting in a trend change, this effect is also prevented by using a constant_offset method.
% 
% ^.

@@

In certain circumstances, the application of the default harmonization methods
can affect not only the magnitude but also the shape of regional
trajectories. Figure \ref{fig:nh3} shows an example case of emissions
trajectories for ammonia (NH3) from the agriculture sector in Asia. Again, the
SAS region shows a large discrepancy in the harmonization year ($>$150\% in
this case). The resulting trajectory harmonized with the default method
(\code{constant_ratio}) provides a large increase after 2080 in the SSP2
reference scenario. Notably, the SSP2-45 scenario is not affected to the same
degree. While this distortion changes the magnitude of the SAS trajectory, it
% * <maarten.vandenberg@pbl.nl> 2017-07-03T22:57:57.074Z:
% 
% > Notably, the SSP2-45 scenario is not affected to the same
% > degree.
% First, I think other effects are in play here. The unharmonized SSP2 -ref scenario has a discontinuity in it's derivative for the SAS region. This is amplified at the regional level by the constant_ratio approach and affects the 4.5 scenario in the same manner, that just happens to lack the discontinuity. Furthermore the trend of other regions is strengthened (a stronger decrease), leading up to an even stronger discontinuity in the global total. However, the ratio approach does a better job at representing the trend in the scenario. That trade-off is not completely clear now, also refers back to goodness of fit. Secondly, more problematic effects occur when applying reduce_ratio methods, that can lead to strong magnitude and trend changes; however this should only occur (significantly) when in override mode (if I understand the implementation of dH correctly).
% 
% ^.
largely affects the post-2080 shape of the global trajectory (see Figure
\ref{fig:nh3}, panel \textbf{c}). By using a \code{constant_offset} method as an
override, this distortion is addressed and more accurately reflects unharmonized
results both in the SAS region and global results for agricultural ammonia
emissions.
